Draft2

### 2022-04-20 Draft2.Rmd
made tables with kable

```{r}
# Want the range 2007-2017 
# took this out c(2007, 2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017)

@@

```

```{r}
#SCRATCH WORK ABOVE

#Not sure if we want to use the selected few countries we looked at earlier?
#Or if we wanted to use this as a overview of the data

#separation by high vs low population among continents 
death_07_high <- deaths_df %>% 
  filter(year == 2007, country %in% c('United States', 'Brazil', 'Ethiopia', 'Russia', 'China', 'Australia')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_07_high = mean(total_deaths))

death_07_low<- deaths_df %>% 
  filter(year == 2007, country %in% c('Canada', 'Argentina', 'Seychelles', 'Romania', 'Israel', 'Tonga')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_07_low = mean(total_deaths))

#Combo table 2007
combo_07<- death_07_high %>% 
  mutate(death_07_low)
combo_07

death_12_high <- deaths_df %>% 
  filter(year == 2012, country %in% c('United States', 'Brazil', 'Ethiopia', 'Russia', 'China', 'Australia')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_12_high = mean(total_deaths))

death_12_low<- deaths_df %>% 
  filter(year == 2012, country %in% c('Canada', 'Argentina', 'Seychelles', 'Romania', 'Israel', 'Tonga')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_12_low = mean(total_deaths))

#Combo table 2012
combo_12<- death_12_high %>% 
  mutate(death_12_low)
combo_12

death_17_high <- deaths_df %>% 
  filter(year == 2017, country %in% c('United States', 'Brazil', 'Ethiopia', 'Russia', 'China', 'Australia')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_17_high = mean(total_deaths))

death_17_low<- deaths_df %>% 
  filter(year == 2017, country %in% c('Canada', 'Argentina', 'Seychelles', 'Romania', 'Israel', 'Tonga')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_17_low = mean(total_deaths))

#Combo table 2017
combo_17<- death_17_high %>% 
  mutate(death_17_low)
combo_17

#Graph selected countries 
#Is there a way to color by low and high and combine the two graphs below?
combo_07 %>% 
  ggplot(aes(x = country, y = average_death_07_low)) + 
  geom_point()

combo_07 %>% 
  ggplot(aes(x = country, y = average_death_07_high)) + 
  geom_point()
```

>>>>

```{r, include=FALSE}
# Want the range 2007-2017 
# took this out c(2007, 2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017)

@@

```
# Separation by Population
```{r, echo=FALSE}
#SCRATCH WORK ABOVE

#Not sure if we want to use the selected few countries we looked at earlier?
#Or if we wanted to use this as a overview of the data
library(knitr)
#install.packages('kableExtra')
library(kableExtra)

#separation by high vs low population among continents 
death_07_high <- deaths_df %>% 
  filter(year == 2007, country %in% c('United States', 'Brazil', 'Ethiopia', 'Russia', 'China', 'Australia')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_07_high = mean(total_deaths))
#death_07_high

death_07_low<- deaths_df %>% 
  filter(year == 2007, country %in% c('Canada', 'Argentina', 'Seychelles', 'Romania', 'Israel', 'Tonga')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_07_low = mean(total_deaths))
#death_07_low

#Side by side table 
#kable(list(death_07_high, death_07_low))
kable(death_07_high) %>% 
  kable_styling(full_width = FALSE, position = 'float_left')
kable(death_07_low) %>% 
  kable_styling(full_width = FALSE, position = 'left')

death_12_high <- deaths_df %>% 
  filter(year == 2012, country %in% c('United States', 'Brazil', 'Ethiopia', 'Russia', 'China', 'Australia')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_12_high = mean(total_deaths))
#death_12_high

death_12_low<- deaths_df %>% 
  filter(year == 2012, country %in% c('Canada', 'Argentina', 'Seychelles', 'Romania', 'Israel', 'Tonga')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_12_low = mean(total_deaths))
#death_12_low

#Combo table 2012
#kable(list(death_12_high, death_12_low))
kable(death_12_high) %>% 
  kable_styling(full_width = FALSE, position = 'float_left')
kable(death_12_low) %>% 
  kable_styling(full_width = FALSE, position = 'left')

death_17_high <- deaths_df %>% 
  filter(year == 2017, country %in% c('United States', 'Brazil', 'Ethiopia', 'Russia', 'China', 'Australia')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_17_high = mean(total_deaths))
#death_17_high

death_17_low<- deaths_df %>% 
  filter(year == 2017, country %in% c('Canada', 'Argentina', 'Seychelles', 'Romania', 'Israel', 'Tonga')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_17_low = mean(total_deaths))
#death_17_low

#Combo table 2017
#kable(list(death_17_high, death_17_low))
kable(death_17_high) %>% 
  kable_styling(full_width = FALSE, position = 'float_left')
kable(death_17_low) %>% 
  kable_styling(full_width = FALSE, position = 'left')

#Graph selected countries 
#Is there a way to color by low and high and combine the two graphs below?
#I removed combo_07 so this might not work...

#combo_07 %>% 
  #ggplot(aes(x = country, y = average_death_07_low)) + 
  #geom_point()

#combo_07 %>% 
  #ggplot(aes(x = country, y = average_death_07_high)) + 
  #geom_point()
```
